Empowering Domain Recursion in Symmetric Weighted First-Order Model Counting

### 2022-01-21 notes/notes.tex
Simplify some stuff in the algorithm

\paragraph{Things I might need to explain.}
\begin{itemize}
\item notation: $\Imm$
\item atom, literal, constant, predicate, variable
\item inequality constraint
\item $\Vars$, $\Vars(c) = \Vars(P) \cup \Vars(N) \cup \Vars(C)$
\item $\Doms$ on both formulas and clauses. $\Doms(c) = \Imm \delta_c$, and $\Doms(\phi) = \bigcup_{c \in \phi} \Doms(c)$.
\item substitution
\item size of a domain, how each domain is partitioned into two during compilation.
\item maybe: notation for partial function, notation for powerset, domain size
\item notation for projection (or avoid it?)
\item $\WMC$
\item constraint removal operation
\item two parts: compilation and inference.
\item introduce and use arrows for bijections, injections, set inclusions, etc.
\item $\emptyset$ for an empty partial map.
\end{itemize}

@@

\paragraph{TODO}
\begin{itemize}
\item later: maybe mathcal instead of mathscr
\item maybe $\pi$ is global enough to have a more unique name
\item maybe $c[\beta, \gamma]$ is better than $c \ast (\beta, \gamma)$
\end{itemize}

@@

\begin{definition}
  A \emph{clause} is a triple $c = (P, N, C, \delta_c)$, where $P$ and $N$ are sets of atoms interpreted as positive and negative literals respectively, $C$ is a set of inequality constraints, and $\delta_c\colon \Vars(c) \to \mathscr{D}$ is a function that maps all variables in $c$ to their domains. Two clauses $c$ and $d = (P', N', C', \delta_d)$ are \emph{isomorphic} (written $c \cong d$) if there is a bijection $\beta\colon \Vars(c) \to \Vars(d)$ such that $c\beta = d\beta$. TODO: we will always use this subscript notation for the $\delta$'s. Equality of clauses is defined in the usual way (i.e., all variables, domains, etc. must match).
\end{definition}

@@

@@

TODO: new node types, their algebraic/graphical representation, what info they hold, and how they're created.

>>>>

\paragraph{Things I might need to explain.}
\begin{itemize}
\item notation: $\Imm$
\item atom, literal, constant, predicate, variable
\item inequality constraint. Notation: $[x \ne y]$, where $x$ is a variable (of the clause), and $y$ is either a variable or a constant.
\item $\Vars$, $\Vars(c) = \Vars(P) \cup \Vars(N) \cup \Vars(C)$
\item $\Doms$ on both formulas and clauses. $\Doms(c) = \Imm \delta_c$, and $\Doms(\phi) = \bigcup_{c \in \phi} \Doms(c)$.
\item substitution
\item size of a domain, how each domain is partitioned into two during compilation.
\item maybe: notation for partial function, notation for powerset, domain size
\item notation for projection (or avoid it?)
\item $\WMC$
\item constraint removal operation
\item two parts: compilation and inference.
\item introduce and use arrows for bijections, injections, set inclusions, etc.
\item $\emptyset$ for an empty partial map.
\end{itemize}

@@

\paragraph{TODO}
\begin{itemize}
\item later: maybe mathcal instead of mathscr
\item maybe $\pi$ is global enough to have a more unique name
\item maybe $c[\beta, \gamma]$ is better than $c \ast (\beta, \gamma)$
\item avoid using lowercase latin letters for everything: capitalise domains and variables
\end{itemize}

@@

\begin{definition}
  A \emph{clause} is a triple $c = (P, N, C, \delta_c)$, where $P$ and $N$ are sets of atoms interpreted as positive and negative literals respectively, $C$ is a set of inequality constraints, and $\delta_c\colon \Vars(c) \to \mathscr{D}$ is a function that maps all variables in $c$ to their domains. Two clauses $c$ and $d = (P', N', C', \delta_d)$ are \emph{isomorphic} (written $c \cong d$) if there is a bijection $\beta\colon \Vars(c) \to \Vars(d)$ such that $c\beta = d\beta$. TODO: we will always use this subscript notation for the $\delta$'s. Equality of clauses is defined in the usual way (i.e., all variables, domains, etc. must match).

  TODO: it's probably enough to say it's a set of literals, a set of constraints, and a $\delta$.
\end{definition}

@@

TODO: introduce the Forclift-style notation (e.g., the compile operator) and the arbitrary formula $\phi$.

\paragraph{Preconditions.} There is a domain $d \in \mathscr{D}$ and an element $e \in d$ such that:
\begin{itemize}
\item for each clause $c = (P, N, C, \delta_c) \in \phi$ and variable $v \in \Vars(c)$, either $\delta_c(v) \ne d$ or $[v \ne e] \in C$;
\item $e$ does not occur in any literal of any clause of $\phi$.
\end{itemize}

NOTE: we know that

\paragraph{Operator.}

@@

TODO: algebraic/graphical representation, what info they hold, and how they're created
